### 2012-07-31 notes/coop.tex
added new notes
Added repeated games

@@

>>>>

\section{Game Thoery}

\subsection{Repeated Games}

In \cite {ShohamLeytonBrown09} section 6.1 there is discussion of repeated games.

When the infinitely repeated game is transformed into extensive form, the result is an infinite tree. So the payoffs cannot be attached to any terminal nodes, nor can they be defined as sum of the payoffs in the stage games )which in general willbe infinite). There are two common ways of defining a player's payoff in an infinitly repeated game to get around this problem.

\emph{Average reward: }
Agent cares more about his well-being in the near term than in the long term.
\begin{equation}\label{eq:average_reward}
\lim \limits_{n \to \infty}\frac{\sum_{j=1}^k r_i^{(j)}}{k}
\end{equation}

\emph{Discount reward: }
Agent cares about the future just as much as he cares about the present.
\begin{equation}\label{eq:discount_reward}
\sum_{j=1}^\infty \beta^j r_i^{(j)} \qquad where \qquad 0 \leq \beta \leq 1
\end{equation}

\subsection{Learning}

\section{Cooperative Games}

@@

\cite {RePEc:eee:gamhes:2} Our social life is conducted almost entirely within the structure of groups of agents: individual consumers are households or families; individual producers are firms which are large coalitions of owners of different factors of production;
